Visualizations for the manuscript

### 2022-04-04 metanalysis_visualization/manuscript_Figures.Rmd
perc_disorder_group_all changed to perc_disorder_group_total_first and country added to one of the plots

```{r Interrupted time series by sex}
quantile_bootstrapped_fitted_sex <- bootstrapped_fitted_sex %>%
  # group_by(time_p, period, plotsLabel, sex) %>%
  group_by(time_p, period,  sex) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")
```

@@

### Disorder group 
```{r}
perc_disorder_group_total_first <- perc_disorder_group_all %>%
  select( - percentage_dg ) %>%
  group_by( time_p, disorder_group ) %>%
  mutate( total_cases = sum( count_icd ), 
          dg_cases = sum( count_dg ), 
          percentage = 100* dg_cases / total_cases, 
          country = "ALL")

perc_disorder_group_total_fix %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = disorder_group )) +
  facet_wrap( ~ disorder_group, scales = "free" ) +
  geom_line( aes(color = disorder_group )) +
  geom_point( aes( color = disorder_group )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA))

percentages_htm <- perc_disorder_group_total %>%
  select( time_p, disorder_group, percentage ) %>%
  unique() %>%
  pivot_wider( names_from =  disorder_group, 
               values_from = percentage )

@@

counts_htm <- perc_disorder_group_total %>%
  select( time_p, disorder_group, dg_cases ) %>%
  unique() %>%
  pivot_wider( names_from =  disorder_group, 
               values_from = dg_cases )
counts_htm <- counts_htm[  , -1]

@@

#### facet wrap in 3 groups based on %
### most prevalent
perc_disorder_group_total %>%
  filter(disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury" ))  %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  facet_wrap( ~ disorder_group ) +
  geom_line( aes(color = country )) +
  geom_point( aes( color = country )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA)) +
  scale_color_manual( values = cbPalette )

#medium prevalent
perc_disorder_group_total %>%
  filter(disorder_group %in% c("Trauma and Stressor-Related Disorders", "Mental Health Symptom", "Disruptive, Impulse Control and Conduct Disorders", 
                               "Feeding and Eating Disorders"))  %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  facet_wrap( ~ disorder_group ) +
  geom_line( aes(color = country )) +
  geom_point( aes( color = country )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA)) +
  scale_color_manual( values = cbPalette )

#low prevalent
perc_disorder_group_total %>%
  filter(disorder_group %in% c("Miscellaneous", "Substance-Related and Addictive Disorders", 
                               "Personality Disorders", "Bipolar and Related Disorders", "Sleep-Wake Disorders", 
                               "Schizophrenia Spectrum and Other Psychotic Disorders", "Somatic Symptom and Related Disorders", 
                               "Obsessive-Compulsive and Related Disorders", "Dissociative Disorders" ))  %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  facet_wrap( ~ disorder_group ) +
  geom_line( aes(color = country )) +
  geom_point( aes( color = country )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA)) +
  scale_color_manual( values = cbPalette )

perc_disorder_group_total %>%
  filter(disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury" ))  %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  facet_wrap( ~ disorder_group ) +
  geom_line( aes(color = country )) +
  geom_point( aes( color = country )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")

perc_disorder_group_total %>%
  filter( disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury", 
  "Mental Health Symptoms", "Feeding and Eating Disorders" )) %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  geom_line( aes(linetype = country, color = country )) +
  geom_point( aes( shape= country, color = country )) +
  #scale_y_continuous(breaks = seq(0, 30, by = 5)) +
  facet_wrap2("disorder_group", axes = "all", scales ="free") + 
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")

@@

numberOfCodesPerDisorderGroup %>%
  mutate( disorder_group = swr( disorder_group ) )  %>%
  ggplot( aes( x= siteid, y = icd_codes_count, fill = country )) +
  geom_bar( stat = "identity") +
  scale_fill_manual("Country of each site", values = c("USA" = "navy", "France" = "orange")) +
  facet_wrap( ~ disorder_group, scales = "free" ) +
  labs(x ="site identifier", y = "ICD dictionary (number of ICD codes)") +
  scale_x_discrete(limits = positions) +
  theme(axis.text.x=element_text(angle=45,hjust=1, size = 6), 
        strip.text = element_text(size = 7), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        legend.position="bottom") 
```

>>>>

```{r Interrupted time series by sex 2}
quantile_bootstrapped_fitted_sex <- bootstrapped_fitted_sex %>%
  # group_by(time_p, period, plotsLabel, sex) %>%
  group_by(time_p, period,  sex) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")
```

@@

### Disorder group 
```{r}
perc_disorder_group_total_first <- perc_disorder_group_all %>%
  select( - percentage_dg ) %>%
  group_by( time_p, disorder_group ) %>%
  mutate( total_cases = sum( count_icd, na.rm = TRUE ), 
          dg_cases = sum( count_dg ), 
          percentage = 100* dg_cases / total_cases, 
          country = "ALL")

perc_disorder_group_total_first %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = disorder_group )) +
  facet_wrap( ~ disorder_group, scales = "free" ) +
  geom_line( aes(color = disorder_group )) +
  geom_point( aes( color = disorder_group )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA))

percentages_htm <- perc_disorder_group_total_first %>%
  select( time_p, disorder_group, percentage ) %>%
  unique() %>%
  pivot_wider( names_from =  disorder_group, 
               values_from = percentage )

@@

counts_htm <- perc_disorder_group_total_first %>%
  select( time_p, disorder_group, dg_cases ) %>%
  unique() %>%
  pivot_wider( names_from =  disorder_group, 
               values_from = dg_cases )
counts_htm <- counts_htm[  , -1]

@@

#### facet wrap in 3 groups based on %
### most prevalent
perc_disorder_group_total_first %>%
  filter(disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury" ))  %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  facet_wrap( ~ disorder_group ) +
  geom_line( aes(color = country )) +
  geom_point( aes( color = country )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA)) +
  scale_color_manual( values = cbPalette )

#medium prevalent
perc_disorder_group_total_first %>%
  filter(disorder_group %in% c("Trauma and Stressor-Related Disorders", "Mental Health Symptom", "Disruptive, Impulse Control and Conduct Disorders", 
                               "Feeding and Eating Disorders"))  %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  facet_wrap( ~ disorder_group ) +
  geom_line( aes(color = country )) +
  geom_point( aes( color = country )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA)) +
  scale_color_manual( values = cbPalette )

#low prevalent
perc_disorder_group_total_first %>%
  filter(disorder_group %in% c("Miscellaneous", "Substance-Related and Addictive Disorders", 
                               "Personality Disorders", "Bipolar and Related Disorders", "Sleep-Wake Disorders", 
                               "Schizophrenia Spectrum and Other Psychotic Disorders", "Somatic Symptom and Related Disorders", 
                               "Obsessive-Compulsive and Related Disorders", "Dissociative Disorders" ))  %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  facet_wrap( ~ disorder_group ) +
  geom_line( aes(color = country )) +
  geom_point( aes( color = country )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA)) +
  scale_color_manual( values = cbPalette )

perc_disorder_group_total_first %>%
  filter(disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury" ))  %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  facet_wrap( ~ disorder_group ) +
  geom_line( aes(color = country )) +
  geom_point( aes( color = country )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")

perc_disorder_group_total_first %>%
  filter( disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury", 
  "Mental Health Symptoms", "Feeding and Eating Disorders" )) %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  geom_line( aes(linetype = country, color = country )) +
  geom_point( aes( shape= country, color = country )) +
  #scale_y_continuous(breaks = seq(0, 30, by = 5)) +
  facet_wrap2("disorder_group", axes = "all", scales ="free") + 
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")

@@

numberOfCodesPerDisorderGroup %>%
  left_join( country_map ) %>%
  mutate( disorder_group = swr( disorder_group ) )  %>%
  ggplot( aes( x= siteid, y = icd_codes_count, fill = country )) +
  geom_bar( stat = "identity") +
  scale_fill_manual("Country of each site", values = c("USA" = "navy", "France" = "orange")) +
  facet_wrap( ~ disorder_group, scales = "free" ) +
  labs(x ="site identifier", y = "ICD dictionary (number of ICD codes)") +
  scale_x_discrete(limits = positions) +
  theme(axis.text.x=element_text(angle=45,hjust=1, size = 6), 
        strip.text = element_text(size = 7), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        legend.position="bottom") 
```
